Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-15 article.tex
Calrification angle et modification détection des villes

    \subsection{Main database}

    This database \cite{main_database} contains all the information needed to the application of the method. It is from
    \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.

@@

\section{Finding the real neighbours}

\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.

@@

\subsection{Measurement of \acrshort{bs} density}
\noindent To simplify the explanation, and because it is related, we will assume that solving this problem is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{clcc}
        \toprule
        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
        \cmidrule(lr){1-4}
        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\subsubsection{Distance criterion}
When looking at the results of Delaunay triangulation, we realise that some edges, mostly on the border of $P$ are too long. Indeed, a \acrshort{bs} does not have an infinite coverage area.

As a consequence, for each \acrshort{bs} the neighbouring connexions that are longer than a certain value, called \emph{max\_distance}, are suppressed (cf. Table~\ref{table:crit_summary}).

\subsubsection{Angle criterion}
For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure~\ref{fig:crit_ang}.

>>>>

    \subsection{Main database}
    This database \cite{main_database} contains all the information needed to the application of the method. It is from
    \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.

@@

\section{Finding the real neighbours}
\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}. However, we know that some of this neighbouring connexions are wrong,
either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.

@@

\subsection{Measurement of \acrshort{bs} density}
\noindent To make it easier to understand, and because it is related,
we will assume that solving this problem is equivalent to finding the \acrshort{bs} situated in \og cities\fg{}.

Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories :
\begin{itemize}
    \item \emph{city center};
    \item \emph{urban area};
    \item \emph{extra-urban area};
    \item \emph{courntryside}.
\end{itemize}

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{lcc}
        \toprule
        \textbf{Description} & \textbf{\emph{max\_distance}} & \textbf{\emph{min\_angle}} \\
        \cmidrule(lr){1-3}
        city center & $\unit[2]{km}$ & $5^\circ$ \\
        urban area & $\unit[5]{km}$ & $10^\circ$ \\
        extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\subsubsection{Distance criterion}
When looking at the results of Delaunay triangulation, we realise that some edges, mostly on the border of $P$ are too long.

Indeed, a \acrshort{bs} does not have an infinite coverage area. As a consequence, for each \acrshort{bs} the neighbouring connexions that are longer than a certain value, called \emph{max\_distance} (cf. Table~\ref{table:crit_summary}), are suppressed.

\subsubsection{Angle criterion}
Let $p$, $q$, $r$ be three \acrshort{bs} of $P$, where $q$ and $r$ are $p$'s potential neighbours. As said before, coverage areas of \acrshort{bs} are limited by physics, this also implies that $r$ can be \og hidden\fg{} from $p$ by $q$ because $q$ is between $p$ and $r$ [trouver qqch pour prouver ce que je dis].

Therefore, the connexion between $p$ and $r$ needs to be suppressed. How? The angle $\widehat{qrp}$ is calculated and if it is narrower than a certain value, called \emph{min\_angle} (cf. Table~\ref{table:crit_summary}), the longest edge is suppressed.
